### 2015-02-18 fundamentals/intro.tex
typo in intro
fixing intro stuff

As nuclear power expands, technical, economic, political, and environmental
analyses of nuclear fuel cycles by simulators increases in importance. The
merits of advanced nuclear technologies and fuel cycles are
shaped by myriad physical, nuclear, chemical, industrial, and political
factors. Nuclear fuel cycle simulators must therefore couple complex models of
nuclear process physics, facility deployment, and material routing. However,
current fuel cycle simulators rely on closed platforms and inflexible
architectures which exhibit three main failure modes. First, they discourage
targeted contribution and collaboration among experts. Next, they hobble
efforts to directly compare modeling methodologies. Finally, they
over-specialize, rendering most tools applicable to only a subset of desired
simulation fidelities, scales, and applications.  The \Cyclus nuclear fuel
cycle simulator framework and its modeling ecosystem incorporate modern
insights from simulation science and software architecture to solve these
problems.  These modern methods simultaneously enable more efficient, accurate,
robust, and validated analysis.

The \Cyclus next-generation fuel cycle simulator is the result of design
choices made to:
\begin{itemize}
\item support access to the tool by fuel cycle analysts and other users,
\item encourage developer extensions,
\item enable plug-and-play comparison of modeling methodologies,
\item and address a range of analysis types, levels of detail, and analyst sophistication.
\end{itemize}

The cardinal purpose of a nuclear fuel cycle simulator is to calculate the
time- and facility-dependent mass flow through all or part the fuel cycle. Many
architecture choices are discussed in \ref{sec:litrev}.  Historically, nuclear
fuel cycle simulators have calculated fuel cycle mass balances and performance
metrics derived from them using software ranging from ad hoc spreadsheet-driven
flow calculators to highly specialized system dynamics modeling platforms. To
date, current tools are often static rather than dynamic, rigid rather than
flexible, fleet-based rather than discrete, or privately distributed rather
than open source. Each of these choices presents a challenge to modeling
fidelity, generality, efficiency, robustness, and scientific transparency.

>>>>

As nuclear power expands, technical, economic, political, and environmental
analyses of nuclear fuel cycles by simulators increase in importance. The
merits of advanced nuclear technologies and fuel cycles are
shaped by myriad physical, nuclear, chemical, industrial, and political
factors. Nuclear fuel cycle simulators must therefore couple complex models of
nuclear process physics, facility deployment, and material routing. However,
current fuel cycle simulators rely on closed platforms and inflexible
architectures which exhibit three main failure modes. First, they discourage
targeted contribution and collaboration among experts. Next, they hobble
efforts to directly compare modeling methodologies. Finally, they
over-specialize, rendering most tools applicable to only a subset of desired
simulation fidelities, scales, and applications.

The \Cyclus nuclear fuel cycle simulator framework and its modeling ecosystem
incorporate modern insights from simulation science and software architecture
to solve these problems.  These modern methods simultaneously enable more
efficient, accurate, robust, and validated analysis.  This next-generation fuel
cycle simulator is the result of design choices made to:

\begin{itemize}
\item support access to the tool by fuel cycle analysts and other users,
\item encourage developer extensions,
\item enable plug-and-play comparison of modeling methodologies,
\item and address a range of analysis types, levels of detail, and analyst sophistication.
\end{itemize}

The cardinal purpose of a nuclear fuel cycle simulator is to calculate the
time- and facility-dependent mass flow through all or part the fuel cycle.
Historically, nuclear fuel cycle simulators have calculated fuel cycle mass
balances and performance metrics derived from them using software ranging from
ad hoc spreadsheet-driven flow calculators to highly specialized system
dynamics modeling platforms. To date, current tools are often static rather
than dynamic, rigid rather than flexible, fleet-based rather than discrete, or
privately distributed rather than open source. Each of these choices presents a
challenge to modeling fidelity, generality, efficiency, robustness, and
scientific transparency.
